---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dezim

<!-- badges: start -->

<!-- badges: end -->

The dezim packages applies the DeZIM style guide formatting and DeZIM colors to ggplot2 graphs.

## Installation

You can install the development version of dezim from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("liamhaller/dezim")
```

## Example

Add \`+ dezim_style() to ggplot2 graphs for DeZIM formatting

```{r example}
library(dezim)
library(ggplot2)

mtcars$gear <- as.factor(mtcars$gear)

p1 <- ggplot(mtcars) +
geom_point(aes(x = wt, y = mpg, colour = gear)) +
labs(
  x = "Weight (1000 lbs)",
  y = "Fuel economy (mpg)",
  colour = "Gears"
  )

# Default Graph
  p1

```

With DeZIM formatting

```{r}
  p1 +
  dezim_style()
```

Finally, use dezim_colors for functions that require color/fill

```{r}
 p1 +
 dezim_style() +
 scale_color_manual(values = dezim_colors)
```

The package also include the function `theme_publish()` to format figures for scientific publications.

```{r}
 p1 +
 theme_publish() 
```
